\textbf{\supplement}\vskip 2ex \mytitle\vskip 2ex

### 2022-01-27 paper-seb-main.tex
Final, as submitted to PLOS ONE

\noindent\emph{Methodology:} This paper samples and reviews software engineering practice in peer reviewed published in leading scientific journals.

\noindent\emph{Results:} On the basis of the sample evidence, scientists rarely assure the quality of any code they rely on, rarely make complete code available, and rarely provide adequate documentation to use code reliably.

>>>>

\noindent\emph{Methodology:} This paper samples and reviews software engineering practice in peer reviewed papers published in leading scientific journals.

\noindent\emph{Results:} On the basis of the sample evidence, scientists rarely assure the quality of any code they rely on, rarely make complete code available, and rarely provide adequate documentation to understand or use code reliably.
